Generating Interactive WebSocket Applications in TypeScript

### 2020-03-09 PLACES_2020/related.tex
PLACES: address reviewers/FZ comments
PLACES: update case study code listing
PLACES: rearrange first sentence under 'Related Work'

\section{Related Work}
Native language support for first-class linear channel resources \cite{ATS} and
code generation are two main approaches for incorporating MPST into application
development.
The latter closely relates to our proposal;
we highlight two areas of existing work under this approach that motivate our
design choice.

\paragraph{Endpoint API Generation}
Neykova and Yoshida targeted Python applications and the generation of runtime
monitors \cite{Python2017} to dynamically verify communication patterns.
Whilst the same approach could be applied to JavaScript, we can provide more
static guarantees with TypeScript's gradual typing system and compiler. Scribble-Java \cite{Hybrid2016} proposed to encode the EFSM
states and transitions as classes and instance methods respectively, with
behavioural typing achieved statically by the type system and channel linearity
guarantees achieved dynamically since channels are exposed and
aliasing is not monitored.

>>>>

\section{Related Work}
The two main approaches for incorporating our MPST workflow into application
development are native language support for first-class linear channel resources \cite{ATS} and code generation.
The latter closely relates to our proposal;
we highlight two areas of existing work under this approach that motivate our
design choice.

\paragraph{Endpoint API Generation}
Neykova and Yoshida targeted Python applications and the generation of runtime
monitors \cite{Python2017} to dynamically verify communication patterns.
Whilst the same approach could be applied to JavaScript, we can provide more
static guarantees with TypeScript's gradual typing system and compiler. Scribble-Java \cite{Hybrid2016} proposed to encode the EFSM
states and transitions as classes and instance methods respectively, with
behavioural typing achieved statically by the type system and channel linearity
guarantees achieved dynamically since channels are exposed and
aliasing is not monitored.
% REVIEW: could the approach of the present paper by applied to Java as well? discuss?
Scribble-Java can generate callback-style APIs similar to the approach we 
present, but this approach is arguably less idiomatic for Java developers.
